|

### 2024-05-31 rmds/figures-supp.Rmd
revisions

```
Figure S1. Convergance success of alternative logistic regression models fit (n = 300) for school shark and gummy shark.

@@

```
Figure S2. Bias (per cent relative error) in parameter estimates of $\hat{L'_{50}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets.

@@

```
Figure S3. Bias (per cent relative error) in parameter estimates of $\hat{P_{Max}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Note 2PLF-maturity and 3PLF-fixed methods both used pre-specified values for $P_{Max}$ and are identical.

@@

```
Figure S4. Accuracy (per cent absolute error) in parameter estimates of $\hat{L'_{50}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets.

@@

```
Figure S5. Accuracy (per cent absolute error) in parameter estimates of $\hat{P_{Max}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Note 2PLF-maturity and 3PLF-fixed methods both used pre-specified values for $P_{Max}$ and are identical. 
\newpage

```{r fig.width = 12, fig.height=7}
ggplot(data %>% filter(par_name %in% "m50", method_long %in% c("3PLF - estimated", "3PLF - fixed"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - Length at 50% maternity")) +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S6. Confidence interval coverage for $L'_{50}$ for 3PLF methods. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. 
\newpage

@@

```
Figure S7. Confidence interval coverage for $P_{Max}$ for the 3PLF-estimated method. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. 
\newpage

@@

```{r fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = "Bias - Reproductive Output") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S10. Bias (per cent relative error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets

@@

```
Figure S11. Accuracy (per cent absolute error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets

@@

Figure S12. Uncropped version of Figure 2. Bias (per cent relative error) in parameter estimates for $\hat{L'_{50}}$ and $\hat{P_{Max}}$ for the 3PLF maternity function with $P_{Max}$ estimated. Each point represents parameter estimates from one iteration of simulated data, including all combinations of variables. Simulations with longer reproductive cycles and fewer maternal females, were associated with higher bias in both parameters $\hat{L'_{50}}$ and $\hat{P_{Max}}$.

>>>>

```
Figure S1. Convergance success of alternative logistic regression models fit (n = 300) for school shark and gummy shark. Point size denotes mean number of females in maternal condition at a given sample size.

@@

```
Figure S2. Bias (per cent relative error) in parameter estimates of $\hat{L'_{50}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Point size denotes mean number of females in maternal condition at a given sample size.

@@

```
Figure S3. Bias (per cent relative error) in parameter estimates of $\hat{P_{Max}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Note 2PLF-maturity and 3PLF-fixed methods both used pre-specified values for $P_{Max}$ and are identical. Point size denotes mean number of females in maternal condition at a given sample size.

@@

```
Figure S4. Accuracy (per cent absolute error) in parameter estimates of $\hat{L'_{50}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Point size denotes mean number of females in maternal condition at a given sample size.

@@

```
Figure S5. Accuracy (per cent absolute error) in parameter estimates of $\hat{P_{Max}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Note 2PLF-maturity and 3PLF-fixed methods both used pre-specified values for $P_{Max}$ and are identical. Point size denotes mean number of females in maternal condition at a given sample size.
\newpage

```{r fig.width = 12, fig.height=7}
ggplot(data %>% filter(par_name %in% "m50", method_long %in% c("3PLF - estimated", "3PLF - fixed"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - Length at 50% maternity")) +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S6. Confidence interval coverage for $L'_{50}$ for 3PLF methods. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. Point size denotes mean number of females in maternal condition at a given sample size.
\newpage

@@

```
Figure S7. Confidence interval coverage for $P_{Max}$ for the 3PLF-estimated method. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. Point size denotes mean number of females in maternal condition at a given sample size.
\newpage

@@

```{r fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = "Bias - Reproductive Output") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S10. Bias (per cent relative error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Point size denotes mean number of females in maternal condition at a given sample size.

```{r}
read_rds(here("data", "simulations-summarised.Rds")) %>% 
  filter(!(method_long %in% "2PLF - maternity" & repro_freq %in% "1 (Annual)")) %>% 
  mutate(Nsamples_sel = fct_cross(factor(mesh_name, levels = c("low", "high")), as.factor(Nsamples))) %>% 
  filter(par_name %in% "r_0") %>% group_by(species, Nsamples_sel, repro_freq) %>% 
  slice_min(abs(rel_error)) %>%
  ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = method_long)) + 
  scale_fill_brewer(palette = "Spectral") + 
  guides(fill = guide_legend(title = "Method")) + 
  facet_wrap(~species, nrow = 1) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```

Figure S11. Performance of alternative maternity functions in minimising bias in calculations of R0. The preferred method was that which minimised bias, |relative error| across 300 simulated datasets. Note 2PLF-maternity (Annual) scenarios were excluded for this comparison.

@@

```
Figure S12. Accuracy (per cent absolute error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Point size denotes mean number of females in maternal condition at a given sample size.

@@

Figure S13. Uncropped version of Figure 2. Bias (per cent relative error) in parameter estimates for $\hat{L'_{50}}$ and $\hat{P_{Max}}$ for the 3PLF maternity function with $P_{Max}$ estimated. Each point represents parameter estimates from one iteration of simulated data, including all combinations of variables. Simulations with longer reproductive cycles and fewer maternal females, were associated with higher bias in both parameters $\hat{L'_{50}}$ and $\hat{P_{Max}}$.

### 2024-05-31 rmds/figures.Rmd
revisions

Figure 2. Bias (per cent relative error) in parameter estimates for $\hat{L'_{50}}$ and $\hat{P_{Max}}$ for the 3PLF maternity function with $P_{Max}$ estimated. Each point represents parameter estimates from one iteration of simulated data (n = 43,129), including all combinations of variables. Simulations with longer reproductive cycles and fewer maternal females were associated with higher bias in both parameters $\hat{L'_{50}}$ and $\hat{P_{Max}}$. Note: 42 data points were cropped to aid with data visualization (see Figure S12 for uncropped figure).\
\
\newpage

@@

```{r fig.width=7, fig.height= 4}
(p <- ggplot(data = data %>% 
  filter(method_long %in% c("3PLF - estimated"), par_name %in% "c"), aes(x = n_maternal, y = abs_error, col = repro_freq)) + 
  geom_point() + 
  scale_color_brewer(palette = "Spectral") +
  scale_y_continuous(breaks = seq(0, 90, 10)) +
  scale_x_continuous(breaks = seq(0, 1600, 200)) +
  facet_grid(~ species) + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  theme_bw() + 
  xlab("Median number of maternal females") + 
  ylab(expression("Mean % absolute error "~hat(italic(P)[Max]))) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center"))
```

>>>>

Figure 2. Bias (per cent relative error) in parameter estimates for $\hat{L'_{50}}$ and $\hat{P_{Max}}$ for the 3PLF maternity function with $P_{Max}$ estimated. Each point represents parameter estimates from one iteration of simulated data (n = 43,129), including all combinations of variables. Simulations with longer reproductive cycles and fewer maternal females were associated with higher bias in both parameters $\hat{L'_{50}}$ and $\hat{P_{Max}}$. Note: 42 data points were cropped to aid with data visualization (see Figure S13 for uncropped figure).\
\
\newpage

@@

```{r fig.width=7, fig.height= 4}

data %>% 
  filter(method_long %in% c("3PLF - estimated"), par_name %in% "c") %>% 
  ggplot() + 
  geom_point(aes(x = n_maternal, y = abs_error, col = repro_freq)) +  
  scale_color_brewer(palette = "Spectral") +
  scale_y_continuous(breaks = seq(0, 90, 10)) +
  scale_x_continuous(breaks = seq(0, 1600, 200)) +
  facet_grid(~ species) + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  theme_bw() + 
  xlab("Median number of maternal females") + 
  ylab(expression("Mean % absolute error "~hat(italic(P)[Max]))) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```

### 2024-05-31 rmds/manuscript.Rmd
revisions

The effect of the different methods in ultimately calculating $R_0$ varied considerably across the various scenarios. For school sharks, estimating $P_{Max}$, was the most effective way to minimize bias in most scenarios (Figure S10). Substituting maturity parameters (2PLF-maturity method) led to a median overestimation of $R_0$ by 3.4% across all scenarios, while the 2PLF-maternity method led to a median underestimate of 11.1%. (Figure S10). In contrast, for the gummy shark substituting maturity parameters led to a median overestimation of $R_0$ of just 1% across all scenarios which outperformed the 3PLF methods in several instances (Figure S10). Using the 2PLF method for gummy sharks led to a median overestimate of $R_0$ of 22% (Figure S10). For both species, better accuracy in calculating $R_0$ was achieved with the 3PLF methods, with the 3PLF-estimated method performing best in most scenarios tested (Figure 6, Figure S11). For gummy sharks the 3PLF-fixed method performed best at lower sample sizes and lower values of $P_{Max}$.

@@

Relatively few reproductive biology studies have used maternity functions to model maternal reproductive output in chondrichthyan fishes. Where they have been employed the approach has typically been to use a three parameter logistic function with a fixed, user-defined value for the upper asymptote, $P_{Max}$. Here we show that it is feasible to estimate $P_{Max}$ from maternal data, in turn enabling statistical inferences on reproductive periodicity. Applying 3PLF models with estimated and fixed values of $P_{Max}$ to simulated data showed that accuracy, bias, and confidence interval coverage often improved when $P_{Max}$ was estimated. Using a fixed value for $P_{Max}$ in some cases resulted in lower bias at low sample sizes. Overall, however, relatively large sample sizes were needed to accurately estimated $P_{Max}$, particularly in species with longer reproductive cycles. This study also demonstrated that, in some cases, recruitment can be overestimated when maturity data were used to approximate maternal data and inaccurate if $P_{Max}$ was ignored when estimating maternity parameters. Based on these findings we outline considerations for practitioners using these methods and illustrate how they can provide novel insights into reproductive biology. We conclude by discussing the advantages of adopting this approach to quantifying maternal reproductive output and future directions.

@@

Using simulated data to compare the relative performance of the 3PLF-estimated and 3PLF-fixed methods subject to a range of variables showed that it was feasible to estimate $P_{Max}$, but was difficult to do so accurately. For non-annual reproductive cycles, $> 100$ school sharks and $> 200$ gummy sharks in maternal condition were typically needed to estimate $P_{Max}$ with \<10% MARE (Figure 5). This indicates that the both sample sizes and levels of uncertainty are likely to be larger than conventional logistic maturity analysis [@roa_estimation_1999]. In the case of the gummy shark this inaccuracy led to the 2PLF-maturity method performing comparably or better than the 3PLF methods in ultimately quantifying $R_0$. Relatively wide confidence intervals were also obtained for $P_{Max}$ in the empirical analysis for sandbar sharks, even with a total sample size of \> 1000 females, of which 206 were in maternal condition. A similar sample size was used by Colonello *et al*. [-@colonello_reproductive_2016] to estimate plausible values of $P_{Max}$ and maternity parameters for south Atlantic spiny dogfish.

@@

For the numerous data-poor chondrichthyan species, or where data on pregnant females are sparse or unattainable, the current practice of using maturity parameters as a proxy for maternity parameters will likely still be the only option. From this perspective, the outperformance of the 3PLF-methods by the 2PLF-methods for the gummy shark in several simulations is encouraging. However, the extent to which maturity parameters can provide a good approximation of maternity parameters may be species-specific, depending on how close $L_{50}$ is to $L'_{50}$. While several studies have shown these parameters to be similar [@walker_spatial_2007; @soto-lopez_reproductive_2018], $L'_{50}$ is more frequently shifted to the right of $L_{50}$ [@braccini_determining_2006; @palacios-hernandez_temporal_2020; @montealegre-quijano_sexual_2014; @colonello_reproductive_2016], and this length difference can equate to one or more years. For example, Harry et al. [-@harry_age_2013] found both spot-tail shark, *C. sorrah*, and Australian blacktip shark, *C. tilstoni*, began reproducing the year after reaching sexual maturity. Similarly, Fujinami et al. [-@fujinami_reproductive_2017] found $A'_{50}$ to be 1.4 years older than $A_{50}$ in blue sharks.

@@

This unexpected result may be related to the gradual attainment of asymptotic maternal status. Maturity in sandbar sharks appears to occur over an extended size range. $L_{5}$ and $L_{95}$ are 146cm and 176cm – a length interval that corresponds to around seven years given the sandbar shark's slow growth rate [@hale_age_2013]. With females maturing over a broad range of sizes and ages, it is possible that smaller females reproduce less frequently. The outcomes of this study suggest that larger sharks may ultimately be capable of reproducing biennially, although few females appear to attain this size [@hale_age_2013]. As such, the modal reproductive frequency is still at least triennial. Further work would be required to confirm this hypothesis, however, such an outcome would have important implications for management; not only are larger females more fecund [@baremore_reproduction_2012], they also reproduce more frequently. This implies that size selective fishing or the removal of larger and older female sharks could have a disproportionately greater impact on population productivity.

@@

One benefit of this approach is that it reduces the need for subjective modelling assumptions relating to $P_{Max}$. Such assumptions can have important implications for population modelling. For example, due to uncertainty in temporal and spatial frequency of reproduction in sparsely-spotted stingarees, *Urolophus paucimaculatus*, Trinnie *et al*. [@trinnie2014] estimated maternity parameters for ten plausible scenarios. In stock assessment of western North Atlantic sandbar sharks a breeding frequency of 2.5 years was assumed to account for uncertainty in the duration of the reproductive cycle [@sedar_sedar_2017].

>>>>

The effect of the different methods in ultimately calculating $R_0$ varied considerably across the various scenarios. For school sharks, estimating $P_{Max}$, was the most effective way to minimize bias in most scenarios (Figure S10). Substituting maturity parameters (2PLF-maturity method) led to a median overestimation of $R_0$ by 3.4% across all scenarios, while the 2PLF-maternity method led to a median underestimate of 11.1%. (Figure S10). In contrast, for the gummy shark substituting maturity parameters led to a median overestimation of $R_0$ of just 1% across all scenarios which outperformed the 3PLF methods in several instances (Figure S11). Using the 2PLF method for gummy sharks led to a median overestimate of $R_0$ of 22% (Figure S10). For both species, better accuracy in calculating $R_0$ was achieved with the 3PLF methods, with the 3PLF-estimated method performing best in most scenarios tested (Figure 6, Figure S12). For gummy sharks the 3PLF-fixed method performed best at lower sample sizes and lower values of $P_{Max}$.

@@

Relatively few reproductive biology studies have used maternity functions to model maternal reproductive output in chondrichthyan fishes. Where they have been employed the approach has typically been to use a three parameter logistic function with a fixed, user-defined value for the upper asymptote, $P_{Max}$. Here we show that it is feasible to estimate $P_{Max}$ from maternal data, in turn enabling statistical inferences on reproductive periodicity. Applying 3PLF models with estimated and fixed values of $P_{Max}$ to simulated data showed that accuracy, bias, and confidence interval coverage often improved when $P_{Max}$ was estimated. Using a fixed value for $P_{Max}$ in some cases reduced bias. Overall, however, relatively large sample sizes were needed to accurately estimate $P_{Max}$, particularly with longer reproductive cycles. This study also demonstrated that, in some cases, recruitment can be overestimated when maturity data were used to approximate maternal data and inaccurate if $P_{Max}$ was ignored when estimating maternity parameters. Based on these findings we outline considerations for practitioners using these methods and illustrate how they can provide novel insights into reproductive biology. We conclude by discussing the advantages of adopting this approach and future directions.

@@

Using simulated data to compare the relative performance of the 3PLF-estimated and 3PLF-fixed methods subject to a range of variables showed that it was feasible to estimate $P_{Max}$, but was difficult to do so accurately. For non-annual reproductive cycles, $> 100$ school sharks and $> 200$ gummy sharks in maternal condition were typically needed to estimate $P_{Max}$ with \<10% MARE (Figure 5). This indicates that the both sample size requirements and levels of uncertainty are likely to be larger than conventional logistic maturity analysis [@roa_estimation_1999]. In the case of the gummy shark this inaccuracy led to the 2PLF-maturity method performing comparably or better than the 3PLF methods in minimizing bias in $R_0$ (Figure S11) Relatively wide confidence intervals were also obtained for $P_{Max}$ in the empirical analysis for sandbar sharks, even with a total sample size of \> 1000 females, of which 206 were in maternal condition. A similar sample size was used by Colonello *et al*. [-@colonello_reproductive_2016] to estimate plausible values of $P_{Max}$ and maternity parameters for south Atlantic spiny dogfish.

@@

For data-poor chondrichthyan species, or where data on pregnant females are sparse or unattainable, the current practice of using maturity parameters as a proxy for maternity parameters will likely still be the only option. From this perspective, the outperformance of the 3PLF-methods by the 2PLF-methods for the gummy shark in several simulations is encouraging. However, the extent to which maturity parameters can provide a good approximation of maternity parameters may be species-specific, depending on how close $L_{50}$ is to $L'_{50}$. While several studies have shown these parameters to be similar [@walker_spatial_2007; @soto-lopez_reproductive_2018], $L'_{50}$ is more frequently shifted to the right of $L_{50}$ [@braccini_determining_2006; @palacios-hernandez_temporal_2020; @montealegre-quijano_sexual_2014; @colonello_reproductive_2016], and this length difference can equate to one or more years. For example, Harry et al. [-@harry_age_2013] found both spot-tail shark, *C. sorrah*, and Australian blacktip shark, *C. tilstoni*, began reproducing the year after reaching sexual maturity. Similarly, Fujinami et al. [-@fujinami_reproductive_2017] found $A'_{50}$ to be 1.4 years older than $A_{50}$ in blue sharks.

@@

This unexpected result may be related to the gradual attainment of asymptotic maternal status. Maturity in sandbar sharks appears to occur over an extended size range. $L_{5}$ and $L_{95}$ are 146cm and 176cm – a length interval that corresponds to around seven years given the sandbar shark's slow growth rate [@hale_age_2013]. With females maturing over a broad range of sizes and ages, it is possible that smaller females reproduce less frequently. The outcomes of this study suggest that larger sharks may ultimately be capable of reproducing biennially. Given that few females appear to attain this size [@hale_age_2013]. this suggests the modal reproductive frequency likely still at least triennial. Further work would be required to confirm this hypothesis, however, such an outcome would have important implications for management; not only are larger females more fecund [@baremore_reproduction_2012], they also reproduce more frequently. This implies that size selective fishing or the removal of larger and older female sharks could have a disproportionately greater impact on population productivity.

@@

One benefit of this approach is that it reduces the need for subjective modelling assumptions relating to $P_{Max}$. Such assumptions can have important implications for population modelling. For example, due to uncertainty in temporal and spatial frequency of reproduction in sparsely-spotted stingarees, *Urolophus paucimaculatus*, Trinnie *et al*. [-@trinnie2014] estimated maternity parameters for ten plausible scenarios. In stock assessment of western North Atlantic sandbar sharks a breeding frequency of 2.5 years was assumed to account for uncertainty in the duration of the reproductive cycle [@sedar_sedar_2017].
